Upgrades to the SINQ Cold Neutron Source

### 2015-09-08 paper.tex
reflectivity graphics

\documentclass[a4paper]{jpconf}
\usepackage{graphicx}
\begin{document}
\title{Upgrades to the SINQ Cold Neutron Source}

@@

model
guide parameters

>>>>

\documentclass[a4paper]{jpconf}
\usepackage{graphicx,amsmath}
\begin{document}
\title{Upgrades to the SINQ Cold Neutron Source}

@@

The guide reflectivity model implmented in MCNP is identical to that used in McStas.  The reflectivity curve for the current guide in the SINQ hall is shown in Figure \ref{SINQ_reflectivity}, along with the reflectivity equation and parameter values shown in Eq. \ref{eq:ref}.

\begin{figure}[h]
\begin{minipage}{14pc}
\includegraphics[scale=.4]{graphics/refl.pdf}
\caption{\label{SINQ_reflectivity} The reflectivity curve of the current SINQ neutron guides.}
\end{minipage}\hspace{5pc}%
\begin{minipage}{11pc}
\begin{multline}\label{eq:ref}\scriptsize
R(Q) = 
\begin{cases}
    \mbox{if } Q > Q_c : \\
    \frac{R_0}{2}\left\{  1 - \tanh\left(  \frac{Q - m Q_c}{W}\right) \right\}\{1-\alpha(Q-Q_c)\} \\
    \\
    \mbox{if } Q \leq Q_c :\\
    R_0 \\
\end{cases} \\ \\ 
\begin{tabular}{c c c}
$R_0=0.995$ & $Q_c=2.17\times10^{-2}\AA^{-1}$ & $m=3.6$ \\ 
$\alpha=3.99 \AA$ & $W=10^{-3} \AA^{-1}$ 
\end{tabular}
\end{multline}
\end{minipage} 
\end{figure}
